---
title: '2016-10-08'
author: "Manvydas Sokolovas"
date: "10/8/2016"
output:
  beamer_presentation:
    keep_tex: yes
---

Reikiamos bibliotekos:
```{r}
library("quantmod")
library("forecast")
library("xts")
library("dplyr")
```


```{r}
data=read.csv("rawdata.csv")

data[ data == ":" ] = NA
data=data[complete.cases(data),]
rownames(data)<-NULL




```


# prasibandymai ir problemos

#(blogas)
mod=lm(monthly.omx~ilgalaikio_vartojimo_prekės+apyvarta+statybu_pasitikejimas+paslaugu_pasitikejimas+vartotoju_pasitikejimas+mazmeninis_pasitikejimas
     +pramones_pasitikejimas+verslo_aktyvumas+turimos_akcijos+uzsakymu_lukesciai+darbolygio_lukesciai+infliacija)

#auto arima?
fit <- auto.arima(monthly.omx, xreg=cbind(apyvarta[-c(length(apyvarta),length(apyvarta)-1),2]))
#tslm?
fit <- tslm(y ~ x) 

```


# prasibandymai ir problemos

#(blogas)
mod=lm(monthly.omx~ilgalaikio_vartojimo_prekės+apyvarta+statybu_pasitikejimas+paslaugu_pasitikejimas+vartotoju_pasitikejimas+mazmeninis_pasitikejimas
     +pramones_pasitikejimas+verslo_aktyvumas+turimos_akcijos+uzsakymu_lukesciai+darbolygio_lukesciai+infliacija)

#auto arima?
fit <- auto.arima(monthly.omx, xreg=cbind(apyvarta[-c(length(apyvarta),length(apyvarta)-1),2]))
#tslm?
fit <- tslm(y ~ x) 
